---
title: "Writeup"
author: "Keri Mallari and Rivka Schuster"
date: "June 28, 2017"
output: html_document
---

Contact info

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
load("colleges.RData")
```

## Introduction
This is a template for a write-up. You can see more advanced ones [here](http://rmarkdown.rstudio.com/developer_document_templates.html) and [here](http://rmarkdown.rstudio.com/gallery.html).

## Data
We used data from the US Department of Education to see the costs of colleges and how the relate to student debt. We divided the colleges into public and private non-profit institutions to see the differences in student debt between the type of institution.

## Analyses
We did a linear regression on the data beause we want to observe the direction of the relationship between cost of college and student debt. The plot below shows the regression model.

```{r plot, echo=FALSE, message=FALSE}
plot(regplot)
```

The p-value was `r Pval` which indicates that institutions with higher costs DO indicate the amount of debt students incur through college. The value of 0 allows us to reject the null hypotheses. 

## Discussion
We think we did a great job. :)

## Appendix
More details about the data.
We registered the study at Microsoft Data Science Summer School